A large-scale analysis of racial disparities in police stops across the United

### 2019-12-11 lib/paper_results.Rmd
updating mj

```{r mj_treatment_search_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_search_rates + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```

@@

```{r mj_treatment_misdemeanor_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_misdemeanor_rates + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```

@@

```{r mj_control_search_rates, fig.height=5, fig.width=10}
mj$plots$control_search_rates
```

>>>>

```{r mj_treatment_search_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_search_rates + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```
```{r mj_treatment_search_rates_counts, fig.height=5, fig.width=10}
mj$plots$treatment_search_rates$counts 
```

@@

```{r mj_treatment_misdemeanor_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_misdemeanor_rates$plot + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```

```{r mj_treatment_misdemeanor_rates_counts, fig.height=5, fig.width=10}
mj$plots$treatment_misdemeanor_rates$counts 
```

@@

```{r mj_control_search_rates_plot, fig.height=5, fig.width=10}
mj$plots$control_search_rates$plot
```

```{r mj_control_search_rates_counts, fig.height=5, fig.width=10}
mj$plots$control_search_rates$counts
```
